Estimation of cloud-corrected microwave humidity radiances with associated uncertainties

### 2020-11-09 Article/ici_submm_cloudcorr_simon.tex
Updated comments.

ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer
Simulator (ARTS, \citet{buehler:artst:18}). CloudSat
\citep{Stephens2002cloudsat} profiles from August 2015 are randomly selected for
forward simulations. The input data are restricted between $60\unit{^{\degree}}S$ to
$60\unit{^{\degree}N}$, and surface is below 500\,m. Both clear-sky and all-sky
scenarios are simulated. The complete simulation setup is described in Appendix
\ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 140\,000 cases are
simulated, respectively. All AWS sensor viewing angles (from $0^\circ$ to
$45^\circ$) are simulated, but the results described in this study are based on
nadir viewing angle. Simulations for all three sensors are noise free, so to
incorporate the measurement uncertainties, whenever needed, gaussian noise is
added to according to the channel NE$\Delta$T (see
Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

@@

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of the NFCS values
described over the chosen quantiles. In order to facilitate the interpretation
of results, examples of QRNN outputs are shown in
Fig.~\ref{fig:posterior_distribution_I1V}. This example illustrates the
predicted quantiles for three different cases. This is in contrast with other
conventional correction/filtering methods, which give out only point estimates.
However, for most application only a single point estimate is required. In
Bayesian analysis, usually the posterior mean or posterior median are selected
as point estimates. In this study, we chose the posterior median as the point
estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN
in correctly predicting the point estimate, deviation of the median value from
the corresponding true value ($\yonfcs$) is evaluated using common performance
indicators like bias, mean absolute error (MAE) and standard deviation (STD).
The asymmetry of error distributions around their mean is also calculated
through the measure of skewness. For a univariate dataset of length $N$, the
Fisher-Pearson coefficient of skewness is defined as:
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.

@@

All evaluation results described in the study have been made on the test dataset.
\todo{Is this true for the hyper parameter tuning? Because if this is the
  case, the evaluation should be redone on independent data.}

@@

\subsection{Experiments}
%
\label{sec:QRNN_expt_MWHS}
For MWHS-2, multiple experiments using both QRNN configurations are performed. With these we aim to delve into the sensitivity of the method to different input channels:

@@

Further we investigated that if filtering the predictions with low accuracy could help in improving the error distributions. For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are cases associated with large deviations. In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed. With 5\,K threshold though the cases with high errors are removed, the persistent negative skewness indicates presence of cases with residual cloud impact. Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases. Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy. For example, for 89+150\,GHz, a threshold of 1.5\,K rejects almost 10\% of data, but the negative skewness is still not completely removed.

@@

\subsubsection{QRNN-single applied to channel 11, 12, 13 and 15}
\label{sec:mwhs_others}
\begin{table*}[t]
	\caption{ Error statisics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz. The labels ``All'' and ``Pred.(5\,K)' are same as described in Table~\ref{tab:error_statistics_mwhs_14}.}
	\label{tab:error_statistics_mwhs_others}
	\begin{tabular}{lrrr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
		\cline{2-6}
		%		\hline
		& &  Clear-sky &   All-sky &  \multicolumn{2}{c}{89+150\,GHz}  \\
		&	&		   &			& All & Pred.(5K)\\
		\middlehline
		Channel 11  &   Bias      & 0.00 &  -0.16 & -0.03 & -0.03(0.2\%)  \\
				    &	MAE       & 0.80 &   0.89 &  0.79 &  0.79  \\
					&	STD       & 1.00 &   1.71 &  1.03 &  1.01  \\
					&	skewness & 0.01 & -20.18 & -0.68 & -0.45  \\
		\middlehline
		Channel 12  & Bias      & -0.00 &  -0.28 & -0.05 & -0.05(0.6\%)  \\
					& MAE       &  0.80 &   0.98 &  0.81 &  0.80  \\
					& STD       &  1.00 &   2.26 &  1.07 &  1.05  \\
					& skewness &  0.00 & -20.72 & -0.91 & -0.70  \\
		\middlehline
		Channel 13  & Bias      & -0.00 &  -0.52 & -0.08 & -0.07(1.6\%)  \\
					& MAE       &  0.80 &   1.17 &  0.84 &  0.83  \\
					& STD       &  1.00 &   3.04 &  1.13 &  1.10  \\
					& skewness &  0.02 & -17.85 & -1.14 & -0.98 \\		
		\middlehline
		Channel 15  & Bias      & -0.00 &  -1.28 & -0.07 & -0.06(5.6\%)  \\
					& MAE       &  0.80 &   1.87 &  0.97 &  0.92 \\
					& STD       &  1.00 &   5.08 &  1.35 &  1.25 \\
					& skewness & -0.00 & -11.15 & -0.60 & -0.83  \\ 
		\bottomhline
	\end{tabular}
\end{table*}
\begin{table*}[t]
	\caption{Channel wise error statistics obtained after filtering MWHS-2 humidity observations  according to scattering index (SI) and filtering described by \citet{buehler:aclou:07}. The latter is denoted as  B183. }
	\label{tab:SI_statistics}
	\begin{tabular}{lrr|rr|rr|rr|rr}
		\tophline
		& \multicolumn{2}{c|}{Channel 11} & \multicolumn{2}{c|}{Channel 12} & \multicolumn{2}{c|}{Channel 13} & \multicolumn{2}{c|}{Channel 14} & \multicolumn{2}{c}{Channel 15}\\
			& SI & B183 & SI & B183 & SI & B183 & SI & B183 & SI & B183\\
			\cline{2-11}
		Bias 	 &-0.04	& -0.05	& -0.07 &  -0.15 &  -0.14 & -0.29	&-0.23 &  -0.51 & -0.33 &  -0.81\\
		MAE  	 & 0.81	&  0.81	&  0.82 &	0.86 &	 0.85 &  0.97   & 0.92 &   1.14 &  1.03 &	1.44\\
		STD  	 &1.02	&  1.03	&  1.04 &	1.14 &	 1.1  &  1.39	& 1.26 &   1.83 &  1.53 &	2.64\\
		Skewness &-0.12 & -0.24 & -0.38 & -0.86  &  -0.91 & -2.23   &-1.79 &  -3.45 & -2.85 &  -4.41\\
		\bottomhline		
	\end{tabular}
\end{table*}

@@

A comparison with SI based filtering and B183 is displayed in  Table~\ref{tab:SI_statistics}. For channel 11 the performance of QRNN is comparable to both SI and B183. Similar is the case with channel 12, though the results from B183 are slightly poor. Both these channels are mostly transparent to hydrometeor impact, and the filtering schemes work well. The major caveat is the rejection of clear cases. With comparable accuracy, the fraction of rejection in SI is approx. 30\% in comparison to approx. 3\% in B183. For channels 13 and 15 the error statistics obtained with SI are slightly inferior in comparison to QRNN. The results with B183 are even worse. For all channels, the two filters succeed in removing the high ice cloud cases, but for lower peaking channels, the high negative skewness values indicate presence of cases with low cloud impact. Clearly the ``one for all'' approach of both filters is not adequate to cater for channel specific hydrometeor impact.

\subsection{Prediction uncertainty}
\label{sec:uncertainty_mwhs}
\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_MWHS_14.pdf}	
	\caption{Examples of prediction uncertainties obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. 1500 randomly selected cases are shown. The quantiles have been plotted at equidistant points. The red line represents a hypothetical Gaussian distribution of $270\pm1.0$\,K.}
	\label{fig:prediction_uncertainty_mwhs}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/calibration_QRNN_MWHS_14.pdf}	
	\caption{Calibration of the prediction intervals obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. Plots for both the complete dataset and the subset with correction greater than 5\,K are shown. }
	\label{fig:calibration_mwhs}	
\end{figure}
\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/deviation_posterior_mwhs_samples_14.pdf}	
	\caption{The distribution of predicted errors and observed errors  obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
	\label{fig:predicted_errors_mwhs}	
\end{figure}

The quantiles given out by QRNN can be used to construct the probability
distribution of the predictions in contrast to other correction approaches which
give out only point estimates. Examples of the uncertainties given out by QRNN
is shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}. The spread of error
distribution is asymmetric. The predictions over quantiles $-3\sigma$,
$-2\sigma$ and $-1\sigma$ are quite sharp and lie close to the median value. In
contrast, the spread of predictions over quantiles $1\sigma$, $2\sigma$ and
$3\sigma$ is wider. Also, cases with very high uncertainty occur infrequently.
The calibration of the prediction intervals on the testing dataset is displayed
in Fig.~\ref{fig:calibration_mwhs}. For the entire dataset, the predictions
follow the y=x line, i.e. the predicted uncertainties are perfectly calibrated
with errors observed on the test data. However for the cases with correction
greater than 5\,K, the distribution is poorly calibrated for higher quantiles.
The curve lies below the y=x line indicating that the prediction intervals are
too narrow. This is in agreement with the wide spread of predictions over the
higher quantiles (Fig.~\ref{fig:prediction_uncertainty_mwhs}). However such
cases are few and filtering them results in well calibrated QRNN predictions.
\todo{This cannot be true. Filtering them, i.e. looking only at values with
  correction < 5k will give predictions with too wide uncertainties, so that the
  calibration will be above the diagonal. I don't think this information is particularly
useful, so I'd suggest removing it.}

@@

\subsection{Prediction accuracy}
\subsubsection{ICI}
%
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels I1V, I2V and I3V.}
	\label{fig:error_distributions}	
\end{figure*}
\begin{table*}[t]
	\caption{ Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for ICI channels I1V, I2V and I3V.}
	\label{tab:error_statistics_ici}
	%	\tabcolsep=0.11cm
	\begin{tabular}{llrr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
		\cline{3-6}
		%		\hline
		&&Clear-sky &   All-sky &  \multicolumn{2}{c}{Predicted}  \\
		&&			   &			&	All & 5\,K \\
		\middlehline
		%		\multicolumn{7}{c}{Channel - I1V}\\

@@

\subsection{Cloud correction with existing sensors}
%
The results from MWHS-2 show that QRNN based cloud correction is partially successful in correcting the cloud impact with existing sensors. The methodology can correctly address the large negative depatures owing to cloud impact, but few cloudy cases end up with inadequate correction. The resulting error distributions are not completely symmetric but have a low bias and spread. Among several input channel combinations described for QRNN-single, the performance of combination 89+150\,GHz is observed to be optimal. The positive performance with 150\,GHz is not unexpected, as 150\,GHz is highly sensitive to ice hydrometeors and cloud water; but using 89\,GHz along with 150\,GHz gives a slightly better performance. The channel 89\,GHz is affected by surface emissivity and is relatively less sensitive to cloud water content, however its sensitivity to warm clouds in the lower troposphere could be important. We also investigate the impact of two temperature sounding channels (MWHS-2 channel 6 and 7). These channels provide complementary information to humidity channels in the lower troposphere. Including both these channels in the training process had no additional effect on the prediction accuracy and almost similar performance as with the combination 89+150\,GHz is obtained.

@@

The partial performance of QRNN is due to incomplete orthogonal information to 183\,GHz channels. The weighting functions of window channels 89 and 150\,GHz, and the two 118\,GHz channels peak in the lower troposphere. Among these four channels, 150\,GHz has the highest peaking function around 4\,km \citep{chen2020mwhs}. These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content upto 2\,km. Due to missing complementary information from other channels in the upper troposphere, QRNN fails at predicting these cases accurately. Such cases are mostly associated with thin cirrus clouds, which have very small influence at 89 and 150\,GHz. Without additional information from other channels we cannot expect QRNN train better. Among the other available channels, the overlapping weighting functions of 183\,GHz can provide auxiliary information to train QRNN. Results show that these channels indeed help in improving the training, yet the non-orthogonal information introduces highly correlated observational errors. The correlations for cloudy observations are not surprising as the cloud amount for different channels depends upon each other in a systematic way. However for clear-sky observations, the correlations should preferably be close to zero. This is observed to be true with QRNN-single, but QRNN-all fails at preserving the noise stochasticity. In the absence of hydrometeor impact, all 183\,GHz channels provide same information to the learning model, introducing redundancy. Redundant patterns in machine learning models often have undesirable effect on the predictive performance. In our application, redundant information does not affect the prediction accuracy, but introduces highly correlated noise between channels. Correlated errors are also undesirable for DA systems, but in future if the operational centres progress with approaches dealing with correlated observation errors, concurrent use of 89, 150 and 183\,GHz channels would give the best cloud correction performance.

@@

Another advantage of QRNN is estimation of case-specific uncertainties. The predictions over chosen quantiles quantify the underlying uncertainty. The analysis of QRNN predicted errors and calibration plots show that QRNN is successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high error. The poorly calibrated predictions are a consequence of cases with different underlying a priori distribution. Predictions with high error originate from cases with high cloud impact or cloudy cases with no orthogonal information. Such cases have a significantly distinct a priori distribution as compared to clear cases, which dominate the training dataset and influence the a priori information. Additional information in form of more observational data or additional training inputs is required to improve QRNN prediction accuracy for such cases. However the cases with low accuracy are associated with high uncertainty, and can be used with caution.  
\todo{I could not follow the last sentence.}

@@

The applicability of QRNN based correction to current sensors is demonstrated with MHWS-2 and it is shown that QRNN is partially successful in removing the cloud impact. This is not  an optimal solution, but it is in agreement with what can be achieved with the present instruments. In comparison to existing clear-filtering approaches, QRNN gives comparable or better performance and with minimal rejection of data. The accuracy of QRNN is affected by one single limitation, that is the prediction of ``out of distribution'' cases. Out of distribution cases are those which belong to a different a priori distribution than the one QRNN is trained on. Such cases can be the ones which occur infrequently, or those which lack any orthogonal information. The representation of the former can be improved with larger training datasets. However for the latter, improving their a priori distribution is not trivial. Correcting hydrometeor impact for cases without complete complementary information is a challenge for QRNN and always limit its performance. \todo{Cases without orthogonal information are note what I understand as out-of-distribution samples. Moreover, rare cases are rather a matter of training set size. Nonetheless, it is of course essential that
  the training set distribution reflects reality.}

>>>>

ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer
Simulator (ARTS, \citet{buehler:artst:18}). CloudSat
\citep{Stephens2002cloudsat} profiles from August 2015 are randomly selected for
forward simulations. The input data are restricted between $60\unit{^{\degree}S}$ to
$60\unit{^{\degree}N}$, and surface is below 500\,m. Both clear-sky and all-sky
scenarios are simulated. The complete simulation setup is described in Appendix
\ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 140\,000 cases are
simulated, respectively. All AWS sensor viewing angles (from $0^\circ$ to
$45^\circ$) are simulated, but the results described in this study are based on
nadir viewing angle. Simulations for all three sensors are noise free, so to
incorporate the measurement uncertainties, whenever needed, gaussian noise is
added to according to the channel NE$\Delta$T (see
Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

@@

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of the NFCS values
described over the chosen quantiles. In order to facilitate the interpretation
of results, examples of QRNN outputs are shown in
Fig.~\ref{fig:posterior_distribution_I1V}. This example illustrates the
predicted quantiles for three different cases. This is in contrast with other
conventional correction/filtering methods, which give out only point estimates.
However, for most applications only a single point estimate is required. In
Bayesian analysis, usually the posterior mean or posterior median are selected
as point estimates. In this study, we chose the posterior median as the point
estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN
in correctly predicting the point estimate, deviation of the median value from
the corresponding true value ($\yonfcs$) is evaluated using common performance
indicators like bias, mean absolute error (MAE) and standard deviation (STD).
The asymmetry of error distributions around their mean is also calculated
through the measure of skewness. For a univariate dataset of length $N$, the
Fisher-Pearson coefficient of skewness is defined as:
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.

@@

All evaluation results described in the study have been made on the test dataset.
\todo{Comment: Is this true for the hyper parameter tuning? Because if this is the
  case, the evaluation should be redone on independent data.}

@@

\subsection{Experiments}
\todo{Comment: I find the structure here confusing. You start with results from channel 14 but then have
  an extra section on the accuracy for channel 14 and then another section considering the other
  channel.}
%
\label{sec:QRNN_expt_MWHS}
For MWHS-2, multiple experiments using both QRNN configurations are performed. With these we aim to delve into the sensitivity of the method to different input channels:

@@

Further we investigated whether filtering the predictions with low accuracy
could help in improving the error distributions. For filtering such cases, we
assume that predictions with cloud correction greater than 5\,K are cases
associated with large deviations. In all three experiments, removing the cases
with correction greater than 5\,K removes around 3\% of the data, but only a
marginal positive impact on the accuracy is observed. With 5\,K threshold though
the cases with high errors are removed, the persistent negative skewness
indicates presence of cases with residual cloud impact. Choosing a lower
threshold can help in removing more partially corrected cases but at the cost of
rejecting clear-sky cases. Since QRNN gives out NFCS values, choosing an
unusually low correction threshold can also classify noisy clear-sky cases as
cloudy. For example, for 89+150\,GHz, a threshold of 1.5\,K rejects almost 10\%
of data, but the negative skewness is still not completely removed.
\todo{Comment: Did you try filtering based on predicted uncertainty?}

@@

\subsubsection{QRNN-single applied to channel 11, 12, 13 and 15}
\label{sec:mwhs_others}
\begin{table*}[t]
	\caption{ Error statisics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz. The labels ``All'' and ``Pred.(5\,K)' are same as described in Table~\ref{tab:error_statistics_mwhs_14}.}
	\label{tab:error_statistics_mwhs_others}
	\begin{tabular}{lrrr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
		\cline{2-6}
		%		\hline
		& &  Clear-sky &   All-sky &  \multicolumn{2}{c}{89+150\,GHz}  \\
		&	&		   &			& All & Pred.(5K)\\
		\middlehline
		Channel 11  &   Bias      & 0.00 &  -0.16 & -0.03 & -0.03(0.2\%)  \\
				    &	MAE       & 0.80 &   0.89 &  0.79 &  0.79  \\
					&	STD       & 1.00 &   1.71 &  1.03 &  1.01  \\
					&	skewness & 0.01 & -20.18 & -0.68 & -0.45  \\
		\middlehline
		Channel 12  & Bias      & -0.00 &  -0.28 & -0.05 & -0.05(0.6\%)  \\
					& MAE       &  0.80 &   0.98 &  0.81 &  0.80  \\
					& STD       &  1.00 &   2.26 &  1.07 &  1.05  \\
					& skewness &  0.00 & -20.72 & -0.91 & -0.70  \\
		\middlehline
		Channel 13  & Bias      & -0.00 &  -0.52 & -0.08 & -0.07(1.6\%)  \\
					& MAE       &  0.80 &   1.17 &  0.84 &  0.83  \\
					& STD       &  1.00 &   3.04 &  1.13 &  1.10  \\
					& skewness &  0.02 & -17.85 & -1.14 & -0.98 \\		
		\middlehline
		Channel 15  & Bias      & -0.00 &  -1.28 & -0.07 & -0.06(5.6\%)  \\
					& MAE       &  0.80 &   1.87 &  0.97 &  0.92 \\
					& STD       &  1.00 &   5.08 &  1.35 &  1.25 \\
					& skewness & -0.00 & -11.15 & -0.60 & -0.83  \\ 
		\bottomhline
	\end{tabular}
\end{table*}
\begin{table*}[t]
	\caption{Channel wise error statistics obtained after filtering MWHS-2 humidity observations  according to scattering index (SI) and filtering described by \citet{buehler:aclou:07}. The latter is denoted as  B183. \todo{Comment: Did you consider combining this with Tab. 5? If combined might be worth highlighting the best performing filtering method. Fraction of filtered cases should have its own column.}}
	\label{tab:SI_statistics}
	\begin{tabular}{lrr|rr|rr|rr|rr}
		\tophline
		& \multicolumn{2}{c|}{Channel 11} & \multicolumn{2}{c|}{Channel 12} & \multicolumn{2}{c|}{Channel 13} & \multicolumn{2}{c|}{Channel 14} & \multicolumn{2}{c}{Channel 15}\\
			& SI & B183 & SI & B183 & SI & B183 & SI & B183 & SI & B183\\
			\cline{2-11}
		Bias 	 &-0.04	& -0.05	& -0.07 &  -0.15 &  -0.14 & -0.29	&-0.23 &  -0.51 & -0.33 &  -0.81\\
		MAE  	 & 0.81	&  0.81	&  0.82 &	0.86 &	 0.85 &  0.97   & 0.92 &   1.14 &  1.03 &	1.44\\
		STD  	 &1.02	&  1.03	&  1.04 &	1.14 &	 1.1  &  1.39	& 1.26 &   1.83 &  1.53 &	2.64\\
		Skewness &-0.12 & -0.24 & -0.38 & -0.86  &  -0.91 & -2.23   &-1.79 &  -3.45 & -2.85 &  -4.41\\
		\bottomhline		
	\end{tabular}
\end{table*}

@@

A comparison with SI based filtering and B183 is displayed in  Table~\ref{tab:SI_statistics}. For channel 11 the performance of QRNN is comparable to both SI and B183. Similar is the case with channel 12, though the results from B183 are slightly poorer. Both these channels are mostly transparent to hydrometeor impact, and the filtering schemes work well. The major caveat is the rejection of clear cases. With comparable accuracy, the fraction of rejection in SI is approx. 30\% in comparison to approx. 3\% in B183. For channels 13 and 15 the error statistics obtained with SI are slightly inferior in comparison to QRNN. The results with B183 are even worse. For all channels, the two filters succeed in removing the high ice cloud cases, but for lower peaking channels, the high negative skewness values indicate presence of cases with low cloud impact. Clearly the ``one for all'' approach of both filters is not adequate to cater for channel specific hydrometeor impact.

\subsection{Prediction uncertainty}
\label{sec:uncertainty_mwhs}
\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_MWHS_14.pdf}	
	\caption{Examples of prediction uncertainties obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. 1500 randomly selected cases are shown. The quantiles have been plotted at equidistant points. The red line represents a hypothetical Gaussian distribution of $270\pm1.0$\,K. \todo{Comment: I suggest adding boxes for each quantile to increase the amount of quantitative information in the plot.}}
	\label{fig:prediction_uncertainty_mwhs}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/calibration_QRNN_MWHS_14.pdf}	
	\caption{Calibration of the prediction intervals obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. Plots for both the complete dataset and the subset with correction greater than 5\,K are shown. }
	\label{fig:calibration_mwhs}	
\end{figure}
\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/deviation_posterior_mwhs_samples_14.pdf}	
	\caption{The distribution of predicted errors and observed errors  obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values. \todo{Comment: I suggest different color for predicted}}
	\label{fig:predicted_errors_mwhs}	
\end{figure}

The quantiles given out by QRNN can be used to construct the probability
distribution of the predictions in contrast to other correction approaches which
give out only point estimates. Examples of the uncertainties given out by QRNN
is shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}. The spread of error
distribution is asymmetric. The predictions over quantiles $-3\sigma$,
$-2\sigma$ and $-1\sigma$ are quite sharp and lie close to the median value. In
contrast, the spread of predictions over quantiles $1\sigma$, $2\sigma$ and
$3\sigma$ is wider. Also, cases with very high uncertainty occur infrequently.
The calibration of the prediction intervals on the testing dataset is displayed
in Fig.~\ref{fig:calibration_mwhs}. For the entire dataset, the predictions
follow the y=x line, i.e. the predicted uncertainties are perfectly calibrated
with errors observed on the test data. However for the cases with correction
greater than 5\,K, the distribution is poorly calibrated for higher quantiles.
The curve lies below the y=x line indicating that the prediction intervals are
too narrow. This is in agreement with the wide spread of predictions over the
higher quantiles (Fig.~\ref{fig:prediction_uncertainty_mwhs}). However such
cases are few and filtering them results in well calibrated QRNN predictions.
\todo{Comment: This cannot be true. Filtering them, i.e. looking only at values with
  correction < 5k will give predictions with too wide uncertainties, so that the
  calibration will be above the diagonal. This is because the two sets are complementary
  and the cases must add up to give the good overall calibration shown above.
  Although, It of course could be that this effect is less evident because the
  number of cases < 5k is so much higher.}

@@

\subsection{Prediction accuracy}
\subsubsection{ICI}
%
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels I1V, I2V and I3V.
    \todo{Comment: I might be worth adding  the calibration of error estimates based of B183 or SI with
      a Gaussian error model. I don't think that the blue curve is so bad, actually, and adding these
    values as reference might help to put the results into context.}}
	\label{fig:error_distributions}	
\end{figure*}
\begin{table*}[t]
	\caption{ Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for ICI channels I1V, I2V and I3V.}
	\label{tab:error_statistics_ici}
	%	\tabcolsep=0.11cm
	\begin{tabular}{llrr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
		\cline{3-6}
		%		\hline
		&&Clear-sky &   All-sky &  \multicolumn{2}{c}{Predicted}  \\
		&&			   &			&	All & 5\,K \\
		\middlehline
		%		\multicolumn{7}{c}{Channel - I1V}\\

@@

\subsection{Cloud correction with existing sensors}
%
The results from MWHS-2 show that QRNN based cloud correction is partially successful in correcting the cloud impact with existing sensors. The methodology can correctly address the large negative depatures owing to cloud impact, but few cloudy cases end up with inadequate correction. The resulting error distributions are not completely symmetric but have a low bias and spread. Among several input channel combinations described for QRNN-single, the performance of combination 89+150\,GHz is observed to be optimal. The positive performance with 150\,GHz is not unexpected, as 150\,GHz is highly sensitive to ice hydrometeors and cloud water; but using 89\,GHz along with 150\,GHz gives a slightly better performance. The channel 89\,GHz is affected by surface emissivity and is less sensitive to cloud water content, however its sensitivity to warm clouds in the lower troposphere could be important. We also investigate the impact of two temperature sounding channels (MWHS-2 channel 6 and 7). These channels provide complementary information to humidity channels in the lower troposphere. Including both these channels in the training process had no additional effect on the prediction accuracy and almost similar performance as with the combination 89+150\,GHz is obtained.

@@

The partial performance of QRNN is due to incomplete orthogonal information to 183\,GHz channels. The weighting functions of window channels 89 and 150\,GHz, and the two 118\,GHz channels peak in the lower troposphere. Among these four channels, 150\,GHz has the highest peaking function around 4\,km \citep{chen2020mwhs}. These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content upto 2\,km. Due to missing complementary information from other channels in the upper troposphere, QRNN fails at predicting these cases accurately. Such cases are mostly associated with thin cirrus clouds, which have very small influence at 89 and 150\,GHz. Without additional information from other channels we cannot expect QRNN to perform better. Among the other available channels, the overlapping weighting functions of 183\,GHz can provide auxiliary information to train QRNN. Results show that these channels indeed help in improving the training, yet the non-orthogonal information introduces highly correlated observational errors. The correlations for cloudy observations are not surprising as the cloud amount for different channels depends upon each other in a systematic way. However for clear-sky observations, the correlations should preferably be close to zero. This is observed to be true with QRNN-single, but QRNN-all fails at preserving the noise stochasticity. In the absence of hydrometeor impact, all 183\,GHz channels provide same information to the learning model, introducing redundancy. Redundant patterns in machine learning models often have undesirable effect on the predictive performance. In our application, redundant information does not affect the prediction accuracy, but introduces highly correlated noise between channels. Correlated errors are also undesirable for DA systems, but in future if the operational centres progress with approaches dealing with correlated observation errors, concurrent use of 89, 150 and 183\,GHz channels would give the best cloud correction performance.

\todo{
    The problem that QRNN faces is more than just incomplete orthogonal information. Even when the information
    in 89 and 150 would be orthogonal it would still not be sufficient to do perfect cloud correction. The reason
    is rather that the problem in general is ill-posed and thus at least under- but probably also over constrained
    (the latter due to measurement noise). 
  }

@@

Another advantage of QRNN is estimation of case-specific uncertainties. The predictions over chosen quantiles quantify the underlying uncertainty. The analysis of QRNN predicted errors and calibration plots show that QRNN is successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high error. The poorly calibrated predictions are a consequence of cases with different underlying a priori distribution. Predictions with high error originate from cases with high cloud impact or cloudy cases with no orthogonal information. Such cases have a significantly distinct a priori distribution as compared to clear cases, which dominate the training dataset and influence the a priori information. Additional information in form of more observational data or additional training inputs is required to improve QRNN prediction accuracy for such cases. However the cases with low accuracy are associated with high uncertainty, and can be used with caution.

@@

The applicability of QRNN based correction to current sensors is demonstrated with MHWS-2 and it is shown that QRNN is partially successful in removing the cloud impact. This is not  an optimal solution, but it is in agreement with what can be achieved with the present instruments. In comparison to existing clear-filtering approaches, QRNN gives comparable or better performance and with minimal rejection of data. The accuracy of QRNN is affected by one single limitation, that is the prediction of ``out of distribution'' cases. Out of distribution cases are those which belong to a different a priori distribution than the one QRNN is trained on. Such cases can be the ones which occur infrequently, or those which lack any orthogonal information. The representation of the former can be improved with larger training datasets. However for the latter, improving their a priori distribution is not trivial. Correcting hydrometeor impact for cases without complete complementary information is a challenge for QRNN and always limit its performance. \todo{Cases without orthogonal information are not what I understand as out-of-distribution samples. Moreover, rare cases are rather a matter of training set size. Nonetheless, it is of course essential that
  the training set distribution reflects reality.}
